Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2015-05-29 tese/arch01.tex
[ADD] modules, changed titles

\subsection{Infrastructure}

The infrastructure is composed by: Ice Server, Web Server, Stream Server, Signaling Server and Test Clients.

@@

For the signaling server there is also no preference between \ac{SIP} and \ac{XMPP}, as both support presence information feature. \ac{SigOfly} could be adopted as well but using it would be irrelevant for the final result of this project. For sake of simplicity and easy deployment the chosen platform chosen is the \emph{Ejabberd} \ac{XMPP} application server since it implements \cite{xep0206} which is crucial for web applications, \emph{Ejabberd}, as said before, is also the \ac{XMPP} server that implements more extensions. For simplicity, \emph{Ejabberd} will be configured as a single node instead a member of cluster.

@@

\subsection{Software}

>>>>

\subsection{Modules}
	Our project is divided into five modules.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.55\textwidth]{figures/archs.png}
	\caption{Project Modules}
\end{figure}

 The Web Server sends Web Pages, containing the other modules information, to the client, after this, the client contacts all the other modules. The ICE server will be used for \ac{NAT} traversal. The Stream Server will be used to record streams for further playback. The signaling server will be responsible for user and calls management. The web server will provide libraries to the client in order to interact with the other modules.

\subsection{Implementation Proposal}
The infrastructure is composed by: Ice Server, Web Server, Stream Server, Signaling Server and Test Clients.

@@

For the signaling server there is also no preference between \ac{SIP} and \ac{XMPP}, as both support presence information feature. \ac{SigOfly} could be adopted as well but using it would be irrelevant for the final result of this project. For sake of simplicity and easy deployment the chosen platform chosen is the \emph{Ejabberd} \ac{XMPP} application server since it implements \cite{xep0206} which is crucial for web applications, \emph{Ejabberd}, as said before, is also the \ac{XMPP} server that implements more extensions. Initially, for simplicity, \emph{Ejabberd} will be configured as a single node instead a member of cluster.

@@

### 2015-05-29 tese/intro.tex
[ADD] modules, changed titles

	With the advent of the telephone network, communications have taken a very important step for us to feel more connected with whom we communicate. Still, only the human voice was not enough, the invention of cameras and their consequent digitization were a huge step for real-time communications.

@@

\subsection{Thesis Contributions} % English

	A web application with an easy to learn user interface will be developed to accomplish our goals. Our application, unnamed yet, is supposed to run on most web browsers that are compatible with JavaScript, \ac{WebRTC}, \ac{HTML}5 and \ac{CSS}3.

@@

\subsection{Article Structure} % English

	The second section is dedicated to related work, which is divided into five subsections. The first subsection describes the problems that real-time communications face on nowadays internet, namely the \ac{IPv4} address exhaustion and the client server model constraints. The second subsection describes the \ac{WebRTC} technology and the protocols needed to implement our project. The third subsection addresses the signaling component which is not defined on \ac{WebRTC} specifications. The fourth subsection presents the evolution of multimedia content until the hypermedia, its capabilities, synchronization mechanisms and interactivity. The  fifth and last subsection explores streaming protocols for non-interactive multimedia and how to introduce the interactive component, another important aspects are the ability to control the time flux of a stream and collaborative application development.

	In the third section we propose an architecture in order to develop our Web Application including all the need infrastructure and software.

	The fourth section describes our work methodology and what is our plan in order to solve our problem.

	The fifth section presents the summary and conclusions of our work.

>>>>

	With the advent of the telephone network, communications have taken a very important step for us to feel more connected with whom we communicate. Still, only the human voice was not enough, the invention of cameras and consequent video digitization were a huge step for real-time communications.

@@

\subsection{Thesis Goals} % English

	A web application with an easy to learn user interface will be developed to accomplish solve our problem. Our application, unnamed yet, is supposed to run on most web browsers that are compatible with JavaScript, \ac{WebRTC}, \ac{HTML}5 and \ac{CSS}3.

@@

\subsection{Document Structure} % English

	Section \ref{related} is dedicated to related work, which is divided into five subsections.

	Section \ref{early} describes the problems that real-time communications face on nowadays internet, namely the \ac{IPv4} address exhaustion and the client server model constraints.

	Section \ref{rtc} describes the \ac{WebRTC} technology and the protocols needed to implement our project.

	Section \ref{signaling} addresses the signaling component which is not defined on \ac{WebRTC} specifications. The fourth subsection presents the evolution of multimedia content until the hypermedia, its capabilities, synchronization mechanisms and interactivity.

	Section \ref{collab} explores streaming protocols for non-interactive multimedia and how to introduce the interactive component, another important aspects are the ability to control the time flux of a stream and collaborative application development.

	In section \ref{arch} we propose an architecture in order to develop our Web Application including all the need infrastructure and software.

	Section \ref{meth} describes our work methodology and what is our plan in order to solve our problem.

	Section \ref{concl} presents the summary and conclusions of our work.
